\chapter{Questionnaire}

\section{Question 1}
During your studies, please select if you have taken any formal/related courses in:
\begin{itemize}
\item Mechanics or Applied Mechanics
\item Mechanism Theory
\item Machine Design
\item Rigid Body Mechanics or Multi-Body Dynamics
\item Modeling and Control of Robot Manipulators
\item Humanoid Robotics
\item Biomechanics
\item Linear Control Theory
\item Non-Linear Control Theory
\item Introduction to Robotics
\item Artificial Intelligence or Machine Learning
\item Linear Algebra
\item Advanced Calculus
\item Probability Theory
\item Object Oriented Programming
\end{itemize}
Additionally, mention your grade along with maximum possible grade in the applicable subjects.

\section{Question 2}
How do you find the overall difficulty level of the exercises? Categorize the exercises.
\begin{itemize}
\item Easy
\item Medium
\item Hard
\end{itemize}

\section{Question 3}
What kind of additional help did you seek while solving the exercises?
\begin{itemize}
\item Textbooks
\item Wikipedia
\item Research papers
\item Other online sources
\item Friends/Colleagues
\end{itemize}

\section{Question 4}
Please categorize your attempt to solve the exercises into:
\begin{itemize}
\item Solved without any external reference
\item Solved with the help of known textbooks
\item Solved with the help of online content (Wikipedia, online blogs etc.)
\item Solved after reading research papers
\end{itemize}
List the exercise numbers in front of each option above.

\section{Question 5}
Please select the programming languages where you have a working knowledge.
\begin{itemize}
\item C/C++
\item Python
\item Matlab
\item Julia
\item Ruby
\item Mathematica
\end{itemize}

\section{Question 6}
Please specify if you have worked with any symbolic manipulation packages.
\begin{itemize}
\item Matlab Symbolic Toolbox
\item Maple
\item Singular
\item Sympy
\end{itemize}

\section{Question 7}
Have you worked with any industrial robot platforms?
\begin{itemize}
\item Universal robots
\item KUKA robots
\item St¨aubli robots
\item PUMA 560
\item Others
\end{itemize}

\section{Question 8}
Have you ever built your own robot as a hobby or group project at the University? If yes, describe your robot and your role in the project.

\section{Question 9}
Have you worked with a version control system? If yes, which one?
\begin{itemize}
\item Git
\item SVN
\end{itemize}

\section{Question 10}
Do you have LateX skills?